### 2017-10-13 Gruba/04-uc.tex

\begin{algorithm}[t]
\begin{small}
\caption{User Clustering in \sys{}}
\label{alg:uc}
\begin{algorithmic}[1]
\State Input: \textit{Feature Data} $F$  of a set of users, the minimum/maximum number of clusters $N_i$ and $N_a$
\State Output: Optimal user clustering result $R$
\vspace{1ex}
\ForAll {$t \in [N_i, N_a]$} \label{enu}
	\State group users into $t$ clusters by $F$; \label{task}
	\State clustering result $R'(t)\ =\ \{(u,\ l(u))\}$ with cluster info $l(u)$ for each user $u$; \label{l}
	\ForAll {$u \in \{u\}$}
		\State in-cluster distance $d_i(u)$ \label{v-b};
		\State out-cluster distance $d_o(u)$;
		\State Silhouette coefficient value $v(u)\ =\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}$; \label{v-e}
	\EndFor
	\State $v(t)\ :=\ Avg\{v(u)\}$; \label{avg}
\EndFor
\If {$v(a)\ =\ \ Max\{v(t)\}$}; \label{opti}
	\State $R$ := $R'(a)$;
\EndIf
\State \bfseries{return} $R$.
\end{algorithmic}
\end{small}
\end{algorithm}

@@

Unlike K-Prototype that supports vector samples in which each dimension is of numerical/categorical, K-Gru could also handle the case where a dimension is one normalized vector.
%
Recall the sample data for User Clustering, i.e., \textit{Feature Data} in form of vectors (see formula \ref{eq:fu-flat}), of which the data type regarding each dimension is shown as Table \ref{tbl:data-type}.

\begin{table}[!htb]
\centering
\begin{small}
%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
\caption{Dimension Types in \textit{Feature Data} Vector}
\vspace{0.3cm}
\label{tbl:data-type}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{type}} & \multicolumn{1}{c}{\textbf{data dimensions}}	\\	\midrule \midrule
numerical data				& $\#R_u$, $\#E_u$, $R_{ee,u}$, $\#B_u$,\\
                            &  $R_{oc,u}$, $\#W_{r,u}$,$\#W_{t,u}$				\\	\midrule
categorical data			& $G_u$,$P_u$,$U_{t,u}$				\\	\midrule
normalized vectors			& $P_{rt,u}$, $P_{rg,u}$,$P_{tt,u}$,$P_{tg,u}$,$P_{f,u}$			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

As aforementioned, the clustering of K-Gru rests on the distance between vector samples, where the dimensions are combined with numbers(normalized to 0-1 range), categories and normalized vectors.
For simplicity, we shall first illustrate the distance calculation of the simple vectors with mono data type on each dimension and then demonstrate that of complex vectors in K-Gru.

Given two numerical vectors $Y'\ = (y'_0, y'_1, ...)$ and $Z'\ = (z'_0, z'_1, ...)$, the \od{} \cite{IEEEexample:books/mk/HanKP2011} between $Y'$ and $Z'$ is given by :
%
\begin{equation}
\label{eq:od}
D_n(Y', Z') = \sum_{\substack{e}} (y_e - z_e)^2
\end{equation}

As to the categorical vectors $Y''\ = (y''_0, y''_1, ...)$ and  $Z''\ = (z''_0, z''_1, ...)$, the \hd{} \cite{IEEEexample:huang1997clustering} of $Y''$ and $Z''$ is:
%
\begin{equation}
\label{eq:hd}
D_h(Y'', Z'') = \sum_{\substack{e}} H_e
\end{equation}
where $H_e$ refers to the \hd{} over each dimension, with $H_e\ =\ 1$ if $y''_e$ and $z''_e$ share the identical value, and $H_e\ =\ 0$ otherwise.

@@

Hence, the said distance regarding the complex vectors ($Y\ =\ (Y_0, Y_1, ...)$ and $Z\ =\ (Z_0, Z_1, ...)$ ) in K-Gru, named \gd{}, could be deduced as:
%
\begin{equation}
\label{eq:gd}
D_g(Y, Z) = \sum_{\substack{e}} G_e
\end{equation}
where the distance on each dimension $G_e$ is given by:
%
\begin{equation}
\label{eq:ge}
G_e =
  \begin{cases}
    (Y_e - Z_e)^2       & \quad \text{if } Y_e/Z_e \text{ is numerical}\\
    H_e\ (1\ or\ 0)       	& \quad \text{if } Y_e/Z_e \text{ is categorical}\\
    1 - Y_e \cdot Z_e  		& \quad \text{if } Y_e/Z_e \text{ is of normalized vector}
  \end{cases}
\end{equation}

@@

In \sys{}, Silhouette coefficient value serves as the fundamental criteria for the optimal clustering selection.
Providing a clustering result, each user is associated with a cluster.

For a given user $u$ of cluster $l$, we employ the vector $Y$ to denote the \textit{Feature Data} as in formula \ref{eq:fu-flat}.

\begin{definition}
\label{def:di}
The in-cluster distance $d_i(u)$ is the average distance to all the other users in the same cluster, i.e., $\forall u'' \in l$ \& $u \neq u''$:
\begin{equation}
	d_i(u) = Avg\{D_g(Y_u, Y_u'')\}
\end{equation}
\end{definition}

\begin{definition}
\label{def:do}
The out-cluster distance $d_o(u)$ is measured as the minimum of the distances $\{d^{\ast}\}$ between $u$ and other clusters ($\forall l' \neq l$), i.e.:
\begin{equation}
	d_o(u) = Min\{d^{\ast}(u, l')\}
\end{equation}
where $d^{\ast}$ is given by:
\begin{equation}
	d^{\ast}(u, l') = Avg\{D_g(Y_u, Y_u')\}\ \forall u' \in l'
\end{equation}
\end{definition}

\begin{definition}
\label{def:coef}
The Silhouette coefficient value $v(u)$ is thus concluded:
\begin{equation}
\label{eq:coef}
v(u)\ =\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}	
\end{equation}
\end{definition}

Intuitively, a good clustering solution should result bigger $d_o$ and smaller $d_i$, such that samples with obvious differences go to various clusters and vice versa.
When $d_o$ is far more than $d_i$, Silhouette coefficient value approaches to 1.
Hence, the larger Silhouette coefficient value is, the better clustering performs, by which the optimal solution is selected.

>>>>

\begin{algorithm}[t]
\begin{small}
\caption{User Clustering in \sys{}}
\label{alg:uc}
\begin{algorithmic}[1]
\State Input: \textit{Feature Data} $F$  of a set of users, the minimum/maximum number of clusters $N_i$ and $N_a$
\State Output: Optimal user clustering result $R$
\vspace{1ex}
\ForAll {$t \in [N_i, N_a]$} \label{enu}
	\State group users into $t$ clusters by $F$; \label{task}
	\State clustering result $R'(t)\ =\ \{(u,\ l(u))\}$ with cluster info $l(u)$ for each user $u$; \label{l}
	\ForAll {$u \in \{u\}$}
		\State in-cluster distance $d_i(u)$ \label{v-b};
		\State out-cluster distance $d_o(u)$;
		\State Silhouette coefficient value $v(u)\ :=\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}$; \label{v-e}
	\EndFor
	\State $v(t)\ :=\ Avg\{v(u)\}$; \label{avg}
\EndFor
\If {$v(a)\ =\ \ Max\{v(t)\}$}; \label{opti}
	\State $R$ := $R'(a)$;
\EndIf
\State \bfseries{return} $R$.
\end{algorithmic}
\end{small}
\end{algorithm}

@@

Unlike K-Prototype that supports vector samples in which each dimension is of numerical/categorical, K-Gru could also handle the case where a dimension is one normalized vector.
%
Recall the sample data for User Clustering, i.e., \textit{Feature Data} in form of vectors (see formula \ref{eq:fu}), of which the data type regarding each dimension is shown as Table \ref{tbl:data-type}.

\begin{table}[!htb]
\centering
\begin{small}
%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
\caption{Dimension Types in \textit{Feature Data} Vector}
%\vspace{0.3cm}
\label{tbl:data-type}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Data Dimensions}}	\\	\midrule \midrule
numerical data				& $\#R_u$, $\#E_u$, $R_{ee,u}$, $\#B_u$,\\
                            &  $R_{oc,u}$, $\#W_{r,u}$,$\#W_{t,u}$				\\	\midrule
categorical data			& $G_u, P_u, U_{t,u}$				\\	\midrule
normalized vectors			& $P_{rt,u}$, $P_{rg,u}$, $P_{tt,u}$, $P_{tg,u}$, $P_{f,u}$			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

As aforementioned, the clustering of K-Gru rests on the distance between vector samples, where the dimensions are combined with numbers (normalized to 0-1 range), categories and normalized vectors. For simplicity, we shall first illustrate the distance calculation of the simple vectors with a mono data type on each dimension, and then demonstrate that of complex vectors.

For numerical vectors $Y'\ = (y'_0, y'_1, \ldots)$ and $Z'\ = (z'_0, z'_1, \ldots)$, the \od{} \cite{IEEEexample:books/mk/HanKP2011} between $Y'$ and $Z'$ is given by :
%
\begin{equation}
\label{eq:od}
D_n(Y', Z') = \sum_{\substack{e}} (y_e - z_e)^2
\end{equation}

For categorical vectors $Y''\ = (y''_0, y''_1, \ldots)$ and  $Z''\ = (z''_0, z''_1, \ldots)$, the \hd{} \cite{IEEEexample:huang1997clustering} of $Y''$ and $Z''$ is:
%
\begin{equation}
\label{eq:hd}
D_h(Y'', Z'') = \sum_{\substack{e}} H_e,
\end{equation}
where $H_e$ refers to the \hd{} over each dimension, with $H_e = 1$ if $y''_e$ and $z''_e$ share the identical value, and $H_e = 0$, otherwise.

@@

Putting these together, the distance regarding the complex vectors $Y\ =\ (Y_0, Y_1, ...)$ and $Z\ =\ (Z_0, Z_1, ...)$ in K-Gru, referred to as \gd{}, is defined as:
%
\begin{equation}
\label{eq:gd}
D_g(Y, Z) = \sum_{\substack{e}} G_e
\end{equation}
where the distance on each dimension $G_e$ is given by:
%
\begin{equation}
\label{eq:ge}
G_e =
  \begin{cases}
    (Y_e - Z_e)^2       &  \text{if } Y_e/Z_e \text{ is numerical}\\
    H_e\ (1\ or\ 0)       	&  \text{if } Y_e/Z_e \text{ is categorical}\\
    1 - Y_e \cdot Z_e  		&  \text{if } Y_e/Z_e \text{ is of normalized vector}
  \end{cases}
\end{equation}

@@

In system \sys{}, the Silhouette coefficient metric serves as the fundamental criteria for deriving an optimal clustering result.
Providing a clustering result, each user is associated with a cluster.

%For a user $u$ of cluster $l$, we employ the vector $Y$ to denote the \textit{Feature Data} as in formula \ref{eq:fu}.

\begin{definition}
\label{def:di}
The in-cluster distance $d_i(u)$ is the average distance to all the other users in the same cluster:
\begin{equation}
	d_i(u) = Avg\{D_g(F_u, F_u'')\ |\ u'' \in l \wedge  u \neq u''\}.
\end{equation}
\end{definition}

\begin{definition}
\label{def:do}
The out-cluster distance $d_o(u)$ is measured as the minimum of the distances $\{d^{\ast}\}$ between $u$ and other clusters:
\begin{equation}
	d_o(u) = Min\{d^{\ast}(u, l')\ |\  l' \neq l \},
\end{equation}
where $d^{\ast}$ is given by:
\begin{equation}
	d^{\ast}(u, l') = Avg\{D_g(Y_u, Y_u') \ | \ u' \in l'\}.
\end{equation}
\end{definition}

\begin{definition}
\label{def:coef}
The Silhouette coefficient value $v(u)$ is defined as:
\begin{equation}
\label{eq:coef}
v(u)\ =\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}.	
\end{equation}
\end{definition}

Intuitively, a good clustering solution should have a bigger $d_o$ and a smaller $d_i$, such that samples with obvious differences go to various clusters and vice versa.
When $d_o$ is far more than $d_i$, Silhouette coefficient value approaches to 1.
Hence, the larger Silhouette coefficient value is, the better clustering performs, by which the optimal solution is selected.
